Wikipedia Text Mining and Entropy Analysis

### 2018-10-05 english_unigram&ce&mi.Rmd
Fixing n difference in slope calculation, otherwise calculation works

>>>>

tkns <- extract_tokens("child", 6, 20, prov_utterances)

new_tkns <- tkns %>% 
    filter(word_order %in% c(1,2)) %>%
    group_by(length, word_order) %>%
    summarise(entropy = entropy(n, unit = "log2"), n = n()) %>%
    spread(word_order, entropy) %>%
    group_by(length) %>%
    mutate(diff = `2` - `1`) %>%
  ggplot(aes(x = length, y = diff)) +
  geom_point(aes(size = n)) +
  geom_smooth(se = F) +
  scale_x_log10()

### 2018-10-05 wiki_entropy.Rmd
Fixing n difference in slope calculation, otherwise calculation works

```{r slope_code, include=FALSE, eval = F}
# extract_stem_tokens <- function(role, min_length, utterances) {
#   
#   REPS <- 100
#   
#   if (role == "child") {
#     lengths <- utterances %>%
#       filter(speaker_role == "Target_Child") %>%
#       mutate(length = str_count(stem, " ") + 1)
# 
#   } else {
#     lengths <- utterances %>%
#       filter(speaker_role != "Target_Child") %>%
#       mutate(length = str_count(stem, " ") + 1)
#   }
#   
#   tokens <- lengths %>% 
#     filter(length >= min_length) %>%
#     mutate(utterance_id = 1:n()) %>%
#     unnest_tokens(word, stem) %>%
#     group_by(utterance_id) %>%
#     mutate(word_order = 1:n()) %>%
#     group_by(length, word_order, word) %>%
#     summarise(n = n()) 
# }

@@

  tokens <- utterances %>% 
    filter(length >= min_length) %>%
    filter(length <= max_length) %>%
    mutate(utterance_id = 1:n()) %>%
    unnest_tokens(word, gloss) %>%
    group_by(utterance_id) %>%
    mutate(word_order = 1:n()) %>%
    group_by(length, word_order, word) %>%
    filter(word_order <= length) %>% 
    summarise(n = n()) 
}

extract_tokens <- function(min_length, max_length, utterances) {

  tokens <- utterances %>% 
    mutate(lengths = str_count(gloss, " ")) %>%
    filter(lengths >= min_length) %>%
    filter(lengths <= max_length) %>%
    mutate(utterance_id = 1:n()) %>%
    unnest_tokens(word, gloss, token = stringr::str_split, pattern = " +") %>%
    group_by(utterance_id) %>%
    mutate(word_order = 1:n()) %>%
    group_by(length, word_order, word) %>%
    filter(word_order <= length) %>% 
    summarise(n = n()) 
}

@@

  tokens <- extract_tokens(min_length, max_length, utterances)

@@

xmf_df <- read_csv("~/Documents/Labwork/Joe/Positional-Information/xmf_df.csv")

#get_slopes("not child", 6, py$xmf_df, "gloss")
gtx <- extract_tokens(6, 25, xmf_df) %>% filter(word != " ") %>% filter(word != "")

@@

second_slopes <- replicate(100, second_slope(gtx)) %>% 
    as_data_frame() %>% View()
    # summarise(mean = mean(value), ci_upper = quantile(value, .975), 
    #           ci_lower = quantile(value, .025))

@@

```{r analyze_entropies, include=FALSE, eval = F}
get_entropies <- function(sen_length, df) {

>>>>

```{r slope_analysis, include=FALSE, eval = F}
# extract_stem_tokens <- function(role, min_length, utterances) {
#   
#   REPS <- 100
#   
#   if (role == "child") {
#     lengths <- utterances %>%
#       filter(speaker_role == "Target_Child") %>%
#       mutate(length = str_count(stem, " ") + 1)
# 
#   } else {
#     lengths <- utterances %>%
#       filter(speaker_role != "Target_Child") %>%
#       mutate(length = str_count(stem, " ") + 1)
#   }
#   
#   tokens <- lengths %>% 
#     filter(length >= min_length) %>%
#     mutate(utterance_id = 1:n()) %>%
#     unnest_tokens(word, stem) %>%
#     group_by(utterance_id) %>%
#     mutate(word_order = 1:n()) %>%
#     group_by(length, word_order, word) %>%
#     summarise(n = n()) 
# }

xmf_df <- read_csv("xmf_df.csv")

#get_slopes("not child", 6, py$xmf_df, "gloss")

sub_tokens <- xmf_df %>% 
     mutate(gloss = str_trim(gloss)) %>%
     mutate(length = str_count(gloss, " +") +1) %>%
     filter(length >= min_length) %>%
     filter(length <= max_length) %>%
     mutate(utterance_id = 1:n())

sub_tokens %>%
     unnest_tokens(word, gloss, token = stringr::str_split, pattern = " +") %>%
     group_by(utterance_id) %>%
     mutate(word_order = 1:n()) %>%
     group_by(utterance_id) %>%
     summarise(n = n()) %>%
     # filter(n != 6) %>%
     left_join(sub_tokens) %>%
     select(gloss, n, length) %>%
     View()

@@

  tokens <- utterances %>% 
    mutate(gloss = str_trim(gloss)) %>%
    mutate(length = str_count(gloss, pattern = " +") + 1) %>% 
    filter(length >= min_length) %>%
    filter(length <= max_length) %>%
    mutate(utterance_id = 1:n()) %>%
    unnest_tokens(word, gloss, token = stringr::str_split, pattern = " +") %>%
    group_by(utterance_id) %>%
    mutate(word_order = 1:n()) %>%
    # group_by(utterance_id) %>%
    group_by(length, word_order, word) %>%
    # filter(word_order <= length) %>% 
    summarise(n = n()) # %>%
    # left_join(utterances) %>%
    # select(gloss, n, length) %>%
    # View()
}

gtx <- extract_wiki_tokens(6, 25, xmf_df) %>% filter(word != " ") %>% filter(word != "")

```{r slope_code}
extract_stem_tokens <- function(role, min_length, utterances) {

  if (role == "child") {
    lengths <- utterances %>%
      filter(speaker_role == "Target_Child") %>%
      mutate(length = str_count(stem, " ") + 1)

} else {
    lengths <- utterances %>%
      filter(speaker_role != "Target_Child") %>%
      mutate(length = str_count(stem, " ") + 1)
}

  tokens <- lengths %>% 
    filter(length >= min_length) %>%
    mutate(utterance_id = 1:n()) %>%
    unnest_tokens(word, stem) %>%
    group_by(utterance_id) %>%
    mutate(word_order = 1:n()) %>%
    group_by(length, word_order, word) %>%
    summarise(n = n()) 
}

extract_gloss_tokens <- function(role, min_length, utterances) {

  if (role == "child") {
    lengths <- utterances %>%
      filter(speaker_role == "Target_Child") %>%
      mutate(length = str_count(gloss, " ") + 1)

} else {
    lengths <- utterances %>%
      filter(speaker_role != "Target_Child") %>%
      mutate(length = str_count(gloss, " ") + 1)
}

  tokens <- lengths %>% 
    filter(length >= min_length) %>%
    mutate(utterance_id = 1:n()) %>%
    unnest_tokens(word, gloss) %>%
    group_by(utterance_id) %>%
    mutate(word_order = 1:n()) %>%
    group_by(length, word_order, word) %>%
    filter(word_order <= length) %>% 
    summarise(n = n()) 
}

@@

  tokens <- extract_wiki_tokens(min_length, max_length, utterances)

@@

xmf_df <- read_csv("xmf_df.csv")

#get_slopes("not child", 6, py$xmf_df, "gloss")
gtx <- extract_wiki_tokens(6, 25, xmf_df) %>% filter(word != " ") %>% filter(word != "")

tokens %>%
    filter(word_order %in% c(1,2)) %>%
    group_by(length, word_order) %>%
    summarise(entropy = entropy(n, unit = "log2"), n = n()) %>%
    spread(word_order, entropy) %>%
    group_by(length) %>%
    mutate(diff = `2` - `1`) %>%
  ggplot(aes(x = length, y = diff)) +
  geom_point(aes(size = n)) +
  geom_smooth(se = F) +
  scale_x_log10() #log length stats

@@

second_slopes <- replicate(100, second_slope(gtx)) %>% 
    as_data_frame() %>% 
    summarise(mean = mean(value), ci_upper = quantile(value, .975), 
             ci_lower = quantile(value, .025))

@@

```{r analyze_entropies, include=FALSE, eval = F}
```{r slope_analysis}
#get_slopes("not child", 6, py$xmf_df, "gloss")
gtx <- extract_gloss_tokens("not child", 6, py$xmf_df)
start_slopes <- replicate(1000, start_slope(gtx)) %>% 
    as_data_frame() %>%
    summarise(mean = mean(value), ci_upper = quantile(value, .975), 
              ci_lower = quantile(value, .025))
print(start_slopes)
```

```{r analyze_entropies, include=FALSE}
get_entropies <- function(sen_length, df) {
